Draft2

### 2022-04-19 Draft2.Rmd
Refined to 6 countries the tables are okay but still questions on graph

## Which country has the greatest number of deaths? The least?

>>>>

## Which country has the greatest number of deaths? The least? (dependent on population)

```{r}
# Want the range 2007-2017 
# took this out c(2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017)

#Maybe try increments...?
#When looking at it you can see a decrease among the three years 
#death_07<- deaths_df %>% 
  #group_by(country) %>% 
  #filter(year == 2007) %>% 
  #select(total_deaths) %>% 
  #summarize(average_death_07 = mean(total_deaths))

#death_12<- deaths_df %>% 
  #group_by(country) %>% 
  #filter(year == 2012) %>% 
  #select(total_deaths) %>% 
  #summarize(average_death_12 = mean(total_deaths))

#death_17<- deaths_df %>% 
  #group_by(country) %>% 
  #filter(year == 2017) %>% 
  #select(total_deaths) %>% 
  #summarize(average_death_17 = mean(total_deaths))

#try to have one cohesive table so it's easier to visualize 
#combo <- death_07 %>% 
  #mutate(death_12) %>% 
  #mutate(death_17)

#combo

#Then graph it 
#Just realized there's 200+ countries....the x-axis looks terrible 
#Would be nice to color by continent but then that would mean going through each country
#ggplot(death_07, aes(x= country, y=average_death_07)) +
  #geom_point() +
  #theme(axis.text.x = element_text(angle = 15)) #yah..no rotation made it worse

#SCRATCH WORK ABOVE

#Not sure if we want to use the selected few countries we looked at earlier?
#Or if we wanted to use this as a overview of the data

#separation by high vs low population among continents 
death_07_high <- deaths_df %>% 
  filter(year == 2007, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_07_high = mean(total_deaths))

death_07_low<- deaths_df %>% 
  filter(year == 2007, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_07_low = mean(total_deaths))

#Combo table 2007
combo_07<- death_07_high %>% 
  mutate(death_07_low)
combo_07

death_12_high <- deaths_df %>% 
  filter(year == 2012, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_12_high = mean(total_deaths))

death_12_low<- deaths_df %>% 
  filter(year == 2012, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_12_low = mean(total_deaths))

#Combo table 2012
combo_12<- death_12_high %>% 
  mutate(death_12_low)
combo_12

death_17_high <- deaths_df %>% 
  filter(year == 2017, country %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_17_high = mean(total_deaths))

death_17_low<- deaths_df %>% 
  filter(year == 2017, country %in% c('Canada', 'Argentina', 'Seychelles', 'Romania', 'Israel', 'Tonga')) %>% 
  group_by(country) %>% 
  select(total_deaths) %>% 
  summarize(average_death_17_low = mean(total_deaths))

#Combo table 2017
combo_17<- death_17_high %>% 
  mutate(death_17_low)
combo_17

#Graph selected countries 
#Is there a way to color by low and high?
combo_07 %>% 
  ggplot(aes(x = country, y = average_death_07_low)) + 
  geom_point()
```
